P.berghei pir analysis

### 2021-03-12 Manuscript_pirAnalysis_Github/Pberghei/Manuscript_Github_Pberghei_pir.Rmd
Change directory

---
title: "P.berghei pir analysis"
author: "Timothy Little"
date: "05/01/2021"
output: 
  html_document:
    toc: true
    number_sections: true
    toc_float:
      collapsed: false
      smooth_scroll: true
---

```{r setup, include=FALSE, message = FALSE}
knitr::opts_chunk$set(echo = FALSE, results = TRUE, message = FALSE, warning = FALSE)
# Set below to your own working directory.
knitr::opts_knit$set(root.dir = 
                       "/Users/littlet/Dropbox (The Francis Crick)/Data/Manuscript_pirAnalysis_Github/Pberghei")
options(scipen = 999) # Means that numbers are displayed normally not as 1e6 (1000000)
# getwd()

>>>>

---
title: "P.berghei pir analysis"
author: "Timothy Little"
date: "12/03/2021"
output: 
  html_document:
    toc: true
    number_sections: true
    toc_float:
      collapsed: false
      smooth_scroll: true
---

```{r setup, include=FALSE, message = FALSE}
knitr::opts_chunk$set(echo = FALSE, results = TRUE, message = FALSE, warning = FALSE)
# Set below to your own working directory.
knitr::opts_knit$set(root.dir = 
                       ".")
options(scipen = 999) # Means that numbers are displayed normally not as 1e6 (1000000)
# getwd()
